Verifying Demonstrations

### 2018-05-30 paper/DB-anon-cred.tex
related work, building blocks

\subsection{Distance bounding anonymous credentials}%
\label{DB-anon-cred}

@@

There is a protocol which provide \ac{DBPK} with all the desired properties 
from above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge, instead of \ac{DBPK}.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie 
protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we 
need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = 
  g^\alpha]\)).
To realize this, we will now introduce such a protocol that will allow us to do 
\ac{DB} anonymous credentials.

@@

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
(It was not secure against terrorist fraud either.)
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an 
impersonating verifier (\ie it is public-key).

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to 
one random value but the verifier sends two challenges.
The verifier presents to the prover which commitment and challenge to use 
during the \ac{DB} phase.

@@

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge we must choose \(k\) logarithmically in the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) in the end of the protocol.
A sequential repetition of protocol will decrease this probability.

The \ac{DB} phase protects against distance fraud.
\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with \(r_i\).

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) bits of the other.
Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting them from the prover.
However at this point the adversary must wait for \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.

The protocol is \ac{DBTF} resistant, if the malicious prover gives both 
responses to the adversary, the adversary can compute the secret key.
This follows from the fact that it is \iac{ZKPK}, \ie there is an extractor that 
can extract the secret.

The protocol is also secure against distance hijacking due to the fact that it 
is the authenticating bit string that is used during the \ac{DB} phase, not the 
challenge bit string as in Brands-Chaum.

>>>>

\subsection{Distance-bounding anonymous credentials}%
\label{DB-anon-cred}

@@

One protocol exists in the literature providing \ac{DBPK} with all the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge, instead of \ac{DBPK}.}.
However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = g^\alpha]\)).
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

@@

\emph{Reattempting a distance-bounding Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.

We present the protocol in \cref{SchnorrFigure}.
The main difference with the original Schnorr protocol is that the prover commits to one random value but the verifier sends two challenges.
The verifier presents to the prover which commitments and challenges to use during the \ac{DB} phase.

@@

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with respect to the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) in the end of the protocol.
A sequential repetition of protocol will decrease this probability.

The \ac{DB} phase protects against distance fraud.
\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with \(r_i\).
The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
Afterwards, the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) bits of the other.
Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting them from the prover.
However, at this point the adversary must wait for \(b_{l+1}\) challenge bits from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.

The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can extract the secret.
The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bit string as in the protocol of Brands-Chaum.

### 2018-05-30 paper/DistanceBounding.tex
related work, building blocks

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent 
relay attacks in contactless communications in which the adversary forwards a 
communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic tools as they are independent 
of the semantics of the messages exchanged, so mechanisms ensuring the physical 
proximity between a verifier and a prover must be used.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account.
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate and in his vicinity.

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using 
    a far-away honest prover.
  \item\acf{DBTF}: a legitimate but malicious prover helps a 
    close-to-the-verifier accomplice to authenticate.
  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the 
    verifier on the distance between them.
  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an 
    honest prover close to the verifier.
  \item \acf{DBIF}: the adversary plays against a simplified version of the 
    protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by 
\citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier 
as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials 
(which we do in \cref{DB-anon-cred}).
The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).

>>>>

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account. 
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate AND in his vicinity.
In this sense, \Ac{DB} protocols combines at the same time the classical properties of authentication protocols with the possibility of verifying the physical proximity.

The main attacks against \ac{DB} protocols can be summarized as follows:
%Seb: the following names of attacks should all have the first letters in capital
\begin{itemize}
  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item \acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
%Seb: the two following properties should be defined more precisely
  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
The choice of the anonymous credential system will affect the properties we require of the \ac{DBPK} (\eg that it must be \iac{PKE} for discrete logarithms).
